Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
reorder explanation of cylinders

\noindent
We do not show the formalization of rings here.
%In our formalization, we also use the notion of a field $\mathcal H$,
%which is a ring with $\alpha \in
%\mathcal H$.
The import ring of sets in our formalization is the ring of measurable cylinders on a product space, which
are defined as follows:

@@

\noindent
In this definition, \leanline{s} is a finite subset of the index set
\leanline{ι}, and for some $S$ in the finite product $\prod_{i \in s}
\alpha_i$, consider the projection $\pi_s : \prod_{i \in \iota}
\alpha_i \to \prod_{i \in s} \alpha_i$, and consider the preimage of
$S$. (This is what the last line in previous definition gives.)  {\color{blue}Note,
however, that \leanline{s} (comprising the potential coordinates where
the cylinder deviates from the whole set) need not be unique. However,
we have

\begin{minted}[highlightlines={1}, framesep = 0pt, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theorem mem_cylinders
  (t : Set ((i : ι) → α i)) :
  t ∈ cylinders α ↔
  ∃ (s S : _) (_ : MeasurableSet S), t = cylinder s S
\end{minted}
By the exists-statement, from this result, we are able to choose a
\leanline{Finset ι}, which can be used. This leads to the definition
of \leanlinecolor{cylinders.finset}, which will be needed below.}

From the definition of a \leanlinecolor{cylinder}, we can define the
set of all measurable cylinders.

@@

The set-system of cylinders is in fact a field, hence a ring and hence
a semi-ring. This means we can prove the following:

>>>>

\noindent
We do not show the formalization of rings here.
The important ring of sets in our formalization is the ring of measurable cylinders on a product space.
A cylinder is defined as follows:

@@

\noindent
In this definition, \leanline{s} is a finite subset of the index set
\leanline{ι}, and for some $S$ in the finite product $\prod_{i \in s}
\alpha_i$, consider the projection $\pi_s : \prod_{i \in \iota}
\alpha_i \to \prod_{i \in s} \alpha_i$, and consider the preimage of
$S$ (This is what the last line in previous definition gives.).
We can define \leanlinecolor{cylinders α}, the set of all measurable cylinders.

@@

Membership of that set is characterized as follows:
\begin{minted}[highlightlines={1}, framesep = 0pt, mathescape, numbersep=5pt, framesep=5mm, bgcolor=mygray]{Lean}
theorem mem_cylinders
  (t : Set ((i : ι) → α i)) :
  t ∈ cylinders α ↔
  ∃ (s S : _) (_ : MeasurableSet S), t = cylinder s S
\end{minted}
\noindent
The finite set \leanline{s} of the potential coordinates where
the cylinder deviates from the whole set needs not be unique.
From the exists-statement of \leanline{mem_cylinders}, we however choose an
arbitrary such \leanline{Finset ι}, called \leanlinecolor{cylinders.finset}.

The set-system of cylinders is in fact a field, hence a ring and
a semi-ring. This means we can prove the following:
